### 2019-04-07 paper/paper.tex
added contributions section

\author{\IEEEauthorblockN{ Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
\IEEEauthorblockA{\textit{Department of Computing Science} \\
\textit{University of Alberta}\\
Edmonton, Canada\\
Email: \{kdehaan,neagu,rsauveho,abram.hindle\}@ualberta.ca}
}

@@

% Footnote should maybe be a full source, or just one link
\begin{abstract}
In recent years, the tools and packages most commonly involved with JavaScript development have evolved rapidly.
Newer packages such as Angular and React have experienced a marked increase in popularity among developers, while libraries such as jQuery
have begun to phase out.\footnote[1]{https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
For this reason, we take a second look at a paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} based on data up to September 2015 to see what has changed, and if previously observed trends have remained constant.
In the original paper, the authors use the \emph{node package manager} (\code{npm}) to gain 
insight into the JavaScript ecosystem as a whole. \code{npm}, a hosting service for JavaScript-based software, has only grown in popularity since
the original paper, with more than three times as many hosted packages (now over 750,000) and over ten times as many weekly package downloads (now over ten billion per week).
Additionally, data collected from projects publicly hosted on \code{GitHub} allow us to observe an alternative measure of popularity. 
Ultimately, this second look aims to discover if recent years have had any significant effects on ecosystem-wide trends, and provide developers with further insight into how packages are used and evolve.
\end{abstract}

@@

\subsection{Research Questions}
\begin{itemize}
  \item

\end{itemize}

>>>>

\author{\IEEEauthorblockN{Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
\IEEEauthorblockA{\textit{Department of Computing Science} \\
\textit{University of Alberta}\\
Edmonton, Canada\\
Email: \{kdehaan,neagu,rsauveho,abram.hindle\}@ualberta.ca}
}

@@

% Footnote should maybe be a full source, or just one link
\begin{abstract}
In recent years, the tools and packages most commonly involved with JavaScript development have evolved rapidly.
Newer packages such as Angular and React have experienced a marked increase in popularity among developers, while frameworks such as jQuery
have begun to phase out.\footnote[1]{https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
For this reason, we take a second look at a 2016 paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} to see what has changed, and if previously observed trends have remained constant.
In the original paper, the authors use the \emph{node package manager} (\code{npm}) to gain 
insight into the JavaScript ecosystem as a whole. \code{npm}, a hosting service for JavaScript-based software, has only grown in popularity since
the original paper, with more than three times as many hosted packages (now over 750,000) and over ten times as many weekly package downloads (now over ten billion per week).
Additionally, data collected from projects publicly hosted on \code{GitHub} allow us to observe an alternative measure of popularity. 
Ultimately, this second look aims to discover if recent years have had any significant effects on ecosystem-wide trends, and provide developers with further insight into how packages are used and evolve.
\end{abstract}

@@

The core contributions we make are as follows:
\begin{itemize}
  \item We replicate and verify the results found in the original paper for the window of October 1\textsuperscript{st} 2010 to September 1\textsuperscript{st} 2015.
  \item We extend the analysis to the time period of September 2\textsuperscript{nd} 2015 to April 1\textsuperscript{st} 2019, and evaluate whether patterns and trends noted in the original paper are still observable.
  \item We investigate whether the continued evolution of the JavaScript package ecosystem has affected the relationships between various measures of package popularity.
  \item We determine if the ongoing maturation of the JavaScript ecosystem has resulted in tangible changes to version numbering or adoption practices.
\end{itemize}
